Coherent optical association of atoms into a single molecule

### 2020-11-24 paper.tex
Update excited state linewidth

In order to calculate the ratio $\Omega_m/\Omega_a$,
we now need to extract $ \Omega_a $.
We do this by measuring the dependence of the Raman Rabi frequency on power and detuning.
% which depends on both $\Omega_m$ and $\Omega_a$.
The Raman Rabi frequency shows a non-linear dependency on the tweezer power
due to the change in the atomic wavefunction caused by
tighter confinement at higher power, as shown in Fig.~\ref{f-det}b.
As discussed before, for weakly interacting particles,
$\Omega_a$ scales as $P^{3/8}$.
However, due to the strong interaction between the two atoms in the $\ket{\uparrow_{\text{Na}}\downarrow_{\text{Cs}}}$ state, this approximation breaks down.
Instead, coupled-channel calculations show that the scaling
is very well approximated by $P^{0.29}$ within the range of confinement in our experiment.
Combined with the standard intensity factor, the Raman Rabi frequency should scale as $P^{1.29}$,
which fits well to our experimental result, as shown in Fig.~\ref{f-det}c.
Similar to the light shift, the detuning dependency of the Raman Rabi frequency
is determined by a constant background component and
a $v'=0$ component that scales as $1/\Delta$.
The $v'=0$ component of the Raman Rabi frequency at our detuning is
$2\pi\times1.02(2)~\mathrm{kHz\cdot mW^{-1.29}}$,
or $2\pi \times 5.6(1)~\mathrm{kHz}$ at $3.75~\mathrm{mW}$ tweezer power.
Together with the $\Omega_m$ measured above, the Rabi frequency, $ \Omega_a $, is
$2\pi \times 12.1(3)~\mathrm{MHz}$.
This gives a matrix-element ratio of $11.6(3)$,
which is in fact better than the theory prediction of $23.8$ (Table \ref{tab:rabi_freqs}).
Therefore, this should not cause the ratio of the Raman Rabi frequency to scattering rate
from the $v'=0$ state to be higher than expected.
Furthermore, we independently measure the natural linewidth of the $v'=0$ excited state to be no larger than $20~\mathrm{MHz}$ using photoassociation (PA) spectroscopy, which cannot explain the excess scattering either.

>>>>

In order to calculate the ratio $\Omega_m/\Omega_a$,
we now need to extract $ \Omega_a $.
We do this by measuring the dependence of the Raman Rabi frequency on power and detuning.
% which depends on both $\Omega_m$ and $\Omega_a$.
The Raman Rabi frequency shows a non-linear dependency on the tweezer power
due to the change in the atomic wavefunction caused by
tighter confinement at higher power, as shown in Fig.~\ref{f-det}b.
As discussed before, for weakly interacting particles,
$\Omega_a$ scales as $P^{3/8}$.
However, due to the strong interaction between the two atoms in the $\ket{\uparrow_{\text{Na}}\downarrow_{\text{Cs}}}$ state, this approximation breaks down.
Instead, coupled-channel calculations show that the scaling
is very well approximated by $P^{0.29}$ within the range of confinement in our experiment.
Combined with the standard intensity factor, the Raman Rabi frequency should scale as $P^{1.29}$,
which fits well to our experimental result, as shown in Fig.~\ref{f-det}c.
Similar to the light shift, the detuning dependency of the Raman Rabi frequency
is determined by a constant background component and
a $v'=0$ component that scales as $1/\Delta$.
The $v'=0$ component of the Raman Rabi frequency at our detuning is
$2\pi\times1.02(2)~\mathrm{kHz\cdot mW^{-1.29}}$,
or $2\pi \times 5.6(1)~\mathrm{kHz}$ at $3.75~\mathrm{mW}$ tweezer power.
Together with the $\Omega_m$ measured above, the Rabi frequency, $ \Omega_a $, is
$2\pi \times 12.1(3)~\mathrm{MHz}$.
This gives a matrix-element ratio of $11.6(3)$,
which is in fact better than the theory prediction of $23.8$ (Table \ref{tab:rabi_freqs}).
Therefore, this should not cause the ratio of the Raman Rabi frequency to scattering rate
from the $v'=0$ state to be higher than expected.
Furthermore, we independently measure the natural linewidth of the $v'=0$ excited state to be no larger than $50~\mathrm{MHz}$ using photoassociation (PA) spectroscopy, which cannot explain the excess scattering either.
